---
title: "Classwork Activity"
author: "Charlize Gutierrez-Lopez"
output: html_notebook
---

```{r}
library(dplyr)
```
# Instructions (Step by Step)

## Step 1: Create fake data
```{r}
# Creating a small fake dataset
set.seed(2073) # allows for reproducibility 

students <- data.frame(
  Name = paste("Student", 1:20),
  StudyHours = round(runif(20, 1, 10), 1),
  Satisfaction = round(rnorm(20, mean = 7, sd = 1.5), 1),
  Major = sample(c("Data Science", "Business Analytics", "Math", "Computer Science"), 20, replace = TRUE)
)

head(students)
```


## Step 2: Drop a column

```{r}
# Remove the Name column

Students_Clean <- students %>%
  select(-Name)

```

```{r}
Students_Clean

```


### Question:
Why might someone drop a column like name or ID from a dataset?

### Answer: Confidential information or it might just not be important. The numerical variables are usually more important.

## Step 3: Visualize
```{r}
library(ggplot2)
```

```{r}
ggplot(Students_Clean, aes(x = Major, y = Satisfaction, fill = Major)) +
  geom_boxplot() +
  labs(
    title = "Student Satisfaction by Major",
    x = "Major",
    y = "Satisfaction (1–10)"
  ) +
  theme_minimal()
```


## Step 4: Explain: Write 2–3 sentences each

### Questions:

1. What pattern or difference do you see in the chart?

The pattern I am seeing is that all of these majors satisfaction level is usually between 6 and 8. Every other major has a mean in the middle of the histograms, except data science, which usually has a lower satisfaction.

2. What might explain it?

Working is usually done more because it is required as opposed to because it is fun. So it is understandable that the satisfaction levels are not 9 or 10. The satisfaction level may be low because of an array of things. For example, company culture.

3. Do you think this chart is accurate?

No. I do not think this chart is accurate.

4. Why? Why not?

Satisfaction is not numerical and can be different for everyone. As a result, I do not think this chart is accurate.

## Step 5: Questions on Git, GitHub and R Markdown

### Questions:

1. What does git add do?


2. What is the difference between git commit and git push?


3. Why is it useful to use GitHub for your code or data projects?


4. How could version control help when collaborating?

5. What is the difference between a code chunk and regular text in R Markdown?


6. How could R Markdown help you explain your analysis to someone else?


### Answers:

Git add stages a file.

Git commit saves staged changes. Git push pushes new commits.

GitHub is useful to use because you can access your project from a different computer or share it with other people.

Version control can help track and manages changes to the code, will also allow people to work on different parts of the code at the same time.

A code chunk allows you to run code in markdown. Regular text will only allow words.

R markdown can include your step by step explanations in between your code in an easy to read manner(as opposed to a bunch of comments in the code that may be hard to follow).

